### 2018-02-15 manuscript.Rnw
ref++

\subsection*{Circadian and sleep analysis}
The packages \texttt{zeitgebr} and \texttt{sleepr} provide tools to analyse circadian behaviours and sleep, respectively.
Together, they offer a suite of methods to compute autocorrelogram, $\chi{}^2$\citationneeded{} and Lomb-Scargle\citationneeded{}
periodograms and find their peaks, score sleep from inactivity (\emph{i.e.} using the ``five-minute rule''), and characterise the architecture of sleep bouts (\emph{e.g.} number, length and latency).

>>>>

\subsection*{Circadian and sleep analysis}
The packages \texttt{zeitgebr} and \texttt{sleepr} provide tools to analyse circadian behaviours and sleep, respectively.
Together, they offer a suite of methods to compute autocorrelogram, $\chi{}^2$\cite{sokolove_chi_1978} and Lomb-Scargle\cite{ruf_lomb-scargle_1999}
periodograms and find their peaks, score sleep from inactivity (\emph{i.e.} using the ``five-minute rule''), and characterise the architecture of sleep bouts (\emph{e.g.} number, length and latency).

### 2018-02-15 manuscript.tex
ref++

We gathered a subset of the data from a recent publication \citationneeded{}, which was gracefully made publicly available by the authors\citationneeded{zenodo}.
It shows that flies, which normally become arrhythmic in a Light-Light (LL) regime, are rhythmic (with an period greater than 24h\TODO{phrasing}) when the gene NKCCox is expressed in clock neurons.
The authors have recorded the activity of both TIM/NKCCOK (NKCCox is expressed in their clock neurons) and NKCCOK/+ (the appropriate control) in LL for six days.
Prior to LL, the animals were recorded for a baseline three or four days in normal LD, 12h:12h, conditions.
Two repetitions were performed resulting in a total of 58 animals.
The \texttt{metadata.csv} file, which describes exhaustively all individuals, as well as all the associated result files can be downloaded on zenodo\citationneeded{ibid}.

>>>>

We gathered a subset of the data from a recent publication \cite{buhl_quasimodo_2016}, which was gracefully made publicly available by the authors\citationneeded{zenodo}.
It shows that flies, which normally become arrhythmic in a Light-Light (LL) regime, are rhythmic (with an period greater than 24h\TODO{phrasing}) when the gene NKCCox is expressed in clock neurons.
The authors have recorded the activity of both TIM/NKCCOK (NKCCox is expressed in their clock neurons) and NKCCOK/+ (the appropriate control) in LL for six days.
Prior to LL, the animals were recorded for a baseline three or four days in normal LD, 12h:12h, conditions.
Two repetitions were performed resulting in a total of 58 animals.
The \texttt{metadata.csv} file, which describes exhaustively all individuals, as well as all the associated result files can be downloaded on zenodo\citationneeded{ibid}.
